---
title: "svglite 1.2.0"
---

Today we are pleased to release a new version of svglite. This release
fixes many bugs, includes new documentation vignettes, and improves
fonts support.

You can install svglite with:

```{r, eval=FALSE}
install.packages("svglite")
```

## Font handling

svglite's font support is now much more flexible thanks to two new
arguments: `system_fonts` and `user_fonts`. These two arguments reflect the
two roles that font play in SVG rendering.

1.  `system_fonts` are needed by the computer creating the SVG file. They 
    control how the standard R font faces (sans plain, serif italic, etc) are 
    mapped to fonts on your computer, and used to compute text size on the plot
    (this is particularly important for `plotmath` layouts).
    
    The defaults `system_fonts` match R as closely as possible, but are not
    great for some langauges. One use of `system_fonts` is to specify fonts 
    with better CJK support:

    ```{r, eval=FALSE}
    svglite("Rplots.svg", system_fonts = list(sans = "Arial Unicode MS"))
    plot.new()
    text(0.5, 0.5, "正規分布")
    dev.off()
    ```

1.  `user_fonts` are needed by the computer rendering the SVG on screen. 
    By default, `system_fonts` also set the `user_fonts`, and you shouldn't
    need to touch this yourself. However, they are needed for perfect 
    reproducibility of generated SVGs, as used by the upcoming 
    [vdiffr package](https://github.com/lionel-/vdiffr) which provide graphical 
    unit tests.

For more details, see `vignette("fonts")`. 

## Text scaling

This update also fixes many bugs. The most important is that text is 
now properly scaled within the plot, and we provide a vignette that 
describes the details: `vignette("scaling")`. It documents, for instance, 
how to include a svglite graphic in a web page with the figure text 
consistently scaled with the surrounding text.

Find a full list of changes in the
[release notes](https://github.com/hadley/svglite/releases/tag/v1.2.0).
