---
output:
  md_document:
    variant: markdown_github
---

```{r, include = FALSE}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

# RSvgDevice

[![Travis-CI Build Status](https://travis-ci.org/mdecorde/RSvgDevice.svg?branch=master)](https://travis-ci.org/mdecorde/RSvgDevice)
[![Coverage Status](https://img.shields.io/codecov/c/github/mdecorde/RSvgDevice/master.svg)](https://codecov.io/github/mdecorde/RSvgDevice?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/RSvgDevice)](http://cran.r-project.org/package=RSvgDevice)

A graphics device that produces clean svg output, suitable for use on the web, and to be edited by hand. Compared to the built-in svg device, this leaves text as is, rather than producing vectorised glyphs. 

## Installation

Install the released version from CRAN with:

```R
install.packages("RSvgDevice")
```

Install the development version from github with:

```R
# install.packages("devtools")
devtools::install_github("mdecorde/RSvgDevice")
```

## Benchmarks

Compared to the base svg device, RSvgDevice is quite a bit faster:

```{r}
library(RSvgDevice)
x <- runif(1e3)
y <- runif(1e3)

system.time({
  devSVG()
  plot(x, y)
  dev.off()
})

system.time({
  svg(onefile = TRUE)
  plot(x, y)
  dev.off()
})
```
