---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# svglite

<!-- badges: start -->

[![R build status](https://github.com/r-lib/svglite/workflows/R-CMD-check/badge.svg)](https://github.com/r-lib/svglite/actions) [![Codecov test coverage](https://codecov.io/gh/r-lib/svglite/branch/master/graph/badge.svg)](https://codecov.io/gh/r-lib/svglite?branch=master) [![CRAN Status Badge](http://www.r-pkg.org/badges/version/svglite)](https://cran.r-project.org/package=svglite) <!-- badges: end -->

svglite is a graphics device that produces clean svg output, suitable for use on the web, or hand editing. Compared to the built-in `svg()`, svglite is considerably faster, produces smaller files, and leaves text as is.

## Installation

svglite is available on CRAN using `install.packages("svglite")`. You can install the development version from github with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("r-lib/svglite")
```

## Benchmarks

Compared to the base svg device, svglite is quite a bit faster:

```{r}
library(svglite)
x <- runif(1e3)
y <- runif(1e3)

tmp1 <- tempfile()
tmp2 <- tempfile()
system.time({
  svglite(tmp1)
  plot(x, y)
  dev.off()
})

system.time({
  svg(tmp2, onefile = TRUE)
  plot(x, y)
  dev.off()
})
```

It also produces considerably smaller files:

```{r}
file.size(tmp1) / 1024
file.size(tmp2) / 1024
```

In both cases, compressing to make `.svgz` is worthwhile:

```{r}
gz <- function(in_path, out_path = tempfile()) {
  out <- gzfile(out_path, "w")
  writeLines(readLines(in_path), out)
  close(out)
  
  invisible(out_path)
}
file.size(gz(tmp1)) / 1024
file.size(gz(tmp2)) / 1024
```
